%\begin{multicols}{2}[\section*{Zora Möller (Anarchiste Saboteur)}]

   REP
   @-rep:	60
   c-rep:	40
   g-rep:	30
   i-rep:	20

---

Gavin Gladwell (Criminal Con Artist)

Sylph Morph
Sylph morphs are tailor-made for media icons, elite socialites, XP stars, models and narcissists. Sylph gene sequences are specifically designed for distinctive good looks. Ethereal and elfin features are common, with slim and lithe bodies.
Striking Looks: The character receives a +10 modifier on social skill tests where the sylph's beauty is an influencing factor. This is only applicable against other biomorphs (but not uplifts).

REP
@-rep:	30
c-rep:	50
f-rep:	30
g-rep:	60
i-rep:	30

EQUIPMENT
Armor: Armor Clothing [4/4]
Primary Weapon: Agonizer Pistol (SA, inflicts pain, target must make WIL Test or immediately flee)
Starting Credit: 1,500
Implants: Basic BioMods, Basic Mesh Inserts, Clean Metabolism, Cortical Stack, Enhanced Pheromones (+10 to in-person social skill tests with other biomorphs)
Gear: None


Gavin was an adolescent when the Fall struck, leaving him an orphaned refugee. Since then, he has grown up and thrived on the fringes of the Planetary Consortium’s hypercorp-based society, making do however he could—which often meant selling himself and/or breaking the law. His quick wit and sly tongue opened up some opportunities, and so Gavin has worked with minor criminal syndicates and independently as a grifter, scammer and petty crook. Gavin was inducted into Firewall when he was unfortunate enough to be the victim of some sort of outbreak on a minor Lunar outpost. The incident was so jarring that Gavin intentionally went to great lengths to have the major details erased from his memory, but he is still plagued by nightmares and a bit of mental instability.
Roleplaying Tips: Gavin is smooth enough to sell water to a fish. In fact, he’s so good at talking people into things that he’s developed an amazing ability to talk himself into things that are not always in his best interest (like working for Firewall). Though he projects a confident façade, Gavin occasionally cracks under pressure.
Special Trait: Paranoid Schizophrenia Disorder—Gavin sometimes hears voices and becomes extremely (and unreasonably) paranoid, especially in situations of high stress.

“You? You couldn't negotiate your way out of a paper bag. Let me do the talking.”

---

Gavin Gladwell (Criminal Con Artist)—After Resleeving in Scene 3
Firewall provides Gavin with a ruster morph for Scene 3.

Background: Fall Evacuee
Faction: Criminal
Sex: Male
Gender Identity: Male

Ruster Morph
Adapted for survival with minimum gear in the partially terraformed Martian environment, these transgenic morphs feature insulated skin for more effective thermoregulation and respiratory system improvements to require less oxygen and filter carbon dioxide, among other mods.

EQUIPMENT
Armor: Body Armor [10/10]
Primary Weapon: Agonizer Pistol (SA, inflicts pain, target must make WIL Test or immediately flee)
Starting Credit: 1,500 (minus any spent in Scenes 1 and 2)
Implants: Basic BioMods, Basic Mesh Inserts, Cortical Stack, Enhanced Respiration, Temperature Tolerance
Gear: Specs (+10 visual Perception Tests)

“How about we put down the weapons and discuss this reasonably?”

---

Ahmir Sektioui (Brinker Security Specialist)

Background: Original Space Colonist
Faction: Brinker
Sex: Neuter
Gender Identity: Male

Bouncer Morph
Bouncers are humans genetically adapted for zero-G and microgravity environments. Their legs are more limber, and their feet can grasp as well as their hands.
Limber: Bouncers are especially flexible and supple, and so receive a +10 modifier on any test involving contortion or flexibility, such as escaping from bonds or squeezing through small spaces.

REP
@-rep:	40
c-rep:	40
i-rep:	20

EQUIPMENT
Armor: Body Armor [10/10]
Primary Weapon: Medium Kinetic Pistol (SA/BF/FA, AP –2, DV 2d10 + 2 ammo 12) with 100 shots regular ammo
Starting Credit: 4,000
Implants: Basic BioMods, Basic Mesh Inserts, Cortical Stack, Grip Pads (+30 Climbing), Oxygen Reserve, Prehensile Feet
Gear: None

Ahmir was one of the millions who took a job as a near-indentured servant in space before the Fall in order to escape crushing poverty on Earth. He has now spent almost two decades working various manual labor and menial jobs around the system. Most recently, he has been hiring himself out as a bodyguard or as ship security for traders and others traveling to and from the far fringes of the solar system. He became involved with Firewall several years back when an associate hired him on as an extra gun on a Firewall-sponsored mission to eradicate an Exhuman faction outpost in the Kuiper Belt. Ahmir is aboard the Scum barge looking for new employment.
Roleplaying Tips: Ahmir is generally quiet and keeps to himself, having spent much time on long journeys and in the isolation of deep space. He is honestly friendly and sociable with others, however, greeting any new friends with a large grin and going out of his way even for complete strangers. Ahmir is a bit of an ascetic and his current morph is neuter-sex, as he considers sexual urges a distraction.

“Please put down the weapon, I do not wish to hurt you.”

---

Ahmir Sektioui (Brinker Security Specialist)—After Resleeving in Scene 3
Firewall provides Ahmir with an arachnoid morph in Scene 3, to provide the team with some additional muscle and firepower.

Background: Original Space Colonist
Faction: Brinker
Sex: Bot
Gender Identity: Male

Arachnoid Morph
Arachnoid robotic shells are 1 meter in length, segmented into two parts, with a smaller head like a spider or termite. They feature four pairs of 1.5-meter-long retractable arms/legs, capable of rotating around the axis of the body, with built-in hydraulics for propelling the bot with small leaps. The manipulator claws on each arm/leg can be switched out with extending mini-wheels for high-speed skating movement. A smaller pair of manipulator arms near the head allows for closer handling and tool use.

EQUIPMENT
Armor: Arachnoid Armor [8/8]
Primary Weapon: Kinetic SMG (SA/BF/FA, AP –2, DV 2d10 + 3, ammo 20) with 100 shots regular ammo
Secondary Weapon: Plasma Rifle (SS, AP –8, DV 3d10 + 12, ammo 10)
Starting Credit: 4,000 (minus any spent in Scene 1 or 2)
Enhancements: Basic Mesh Inserts, Cortical Stack, Cyberbrain, Enhanced Vision (+20 to visual Perception Tests), Extra Limbs (6 Arms/Legs), Lidar, Pain Filter (ignore wound modifiers, but they suffer –30 on any tactile-based Perception Tests and will not even notice they have been damaged unless they succeed in a Perception Test), Pneumatic Limbs (can leap 2 meters up, +20 Freerunning Tests, +1d10 DV when used in Unarmed Combat), Radar, Reflex Boost (+10 REF, +1 Speed)
Gear: Nanobandage (heal 1 wound and 1d10 DUR in 1 hour)

“Take cover, this is going to heat things up.”

---

Elis Menezes (Scum Techie)

Background: Reinstantiated
Faction: Scum
Sex: Female
Gender Identity: Female

Splicer Morph
Splicers are genefixed humans. Their genome has been cleansed of hereditary diseases and optimized for looks and health, but has not otherwise been substantially upgraded.

REP
@-rep:	60
i-rep:	40

EQUIPMENT
Armor: Light Smartfabric Vacsuit [5/5]
Primary Weapon: Shock Gloves (use Unarmed Combat skill, target makes DUR + Energy Armor Test or is incapacitated for 1 Action Turn per 10 points of MoF)
Starting Credit: 4,000
Implants: Basic BioMods, Basic Mesh Inserts, Cortical Stack
Gear: Utilitool (+10 Hardware Tests)

Elis died on Earth during the Fall, but a backup of her mind was transmitted off-world. She spent several years as an infugee in cold storage in the Jovian Republic before being revived and re-sleeved in a cheap synthetic morph, the cost of which she had to pay off by helping to build new habitats. Desperate to escape her situation, Elis volunteered to the Gatekeeper Corp and was selected to be a gatecrasher. She survived three missions, one of which brought her into contact with the relics of a long-dead alien race, which resulted into her being recruited into Firewall. After retiring from gatecrashing, Elis found a berth aboard the Ecstatic Metamorphosis and immersed herself in Scum culture, trading her tech service skills for her wants and needs.
Roleplaying Tips: Elis has a multifaceted personality. She can take hardship like a pro, and is more than willing to let her hair down and party away when she gets a breather. She likes to get dressed up and glam herself out with exotic bodytints, nanotats, piercings, and other body mods, but she’s also willing to spend all day taking apart an air compressor with grease up to her elbows. She’s a flagrant abuser of social networks. 

“This piece is totally glitched. Let me grab another beer before I hit it.”

---

Elis Menezes (Scum Techie)—After Resleeving in Scene 3
Firewall provides Elis with a ruster morph for Scene 3.

Background: Reinstantiated
Faction: Scum
Sex: Female
Gender Identity: Female

Ruster Morph
Adapted for survival with minimum gear in the partially terraformed Martian environment, these transgenic morphs feature insulated skin for more effective thermoregulation and respiratory system improvements to require less oxygen and filter carbon dioxide, among other mods. 

EQUIPMENT
Armor: Body Armor [10/10]
Primary Weapon: Shredder (Flechette Spray Weapon, SA/BF/FA, AP –10, DV 2d10 + 5, ammo 100)
Starting Credit: 4,000 (minus any spent in Scene 1 or 2) 
Implants: Basic BioMods, Basic Mesh Inserts, Cortical Stack, Enhanced Respiration, Temperature Tolerance
Gear: Nanocable Spindle, Portable Nanofabricator, Repair Spray (+20 to Hardware Tests), Shelter Dome, Specs (+10 visual Perception Tests)

“Sure, I can fix that, but you'll owe me a dance. A sexy dance.”

\end{document}
